Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-16 doc/reviews/ResponseToReviewer1.tex

\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 1}
\noindent
\comment{Overall, the paper is original and interesting. The derivation
of the hydrophobic force without singular integrals is smart and well
written. The characterization of the effective properties of the
coarse-grained vesicles is also of interest and carefully conducted.
However, in many instances the manuscript looks more like a catalogue of
the different behaviors JP vesicles can exhibit in linear flows, rather
than a comprehensive study. The authors describe a few interesting
phenomena but only partially address the exciting physical questions
related to them. The paper lacks quantitative comparisons with continuum
models, parametric studies and detailed explanations to meet the
standards of JFM. In addition, the manuscript seems to have been written
in haste: a figure with no apparent connection to the content of the
paper has been inserted without being referenced or discussed in the
text (see below), some parts need some serious proofreading and
additional clarifications.}
\begin{itemize}
  \item {\bf Response to Summary}: 	We thank the Reviewer for the assessment of our manuscript submission. In response
to the comments, we have undertaken a major revision in including parametric studies and quantitative comparisons between models. We performed a number of simulations 
in studies of inter-monolayer friction coefficients and an additional numerical investigation 
of permeabilities. We have ensured that all figures are connected with the corresponding content. 
  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
  \end{quotation}
\end{itemize}

@@

\noindent
\comment{There is no parametric study of the effect of the particle size
on the effective properties of the vesicles (interlayer friction,
stretching modulus, permeability,etc$\ldots$). The authors defer this
part for future work in the conclusions, but since the effect of the
particle size is important, as evidenced in Section 4.3, it should be
explored and explained more thoroughly in the manuscript, otherwise the
research would be too incremental. The effect of particle shape seems
indeed more complex and out of the scope of the current paper.}
\begin{itemize}
  \item Response: This comment encouraged us to present more convergence studies in the choices of model parameters. We made a worthwhile effort to perform a large number of simulations. We agree with the Reviewer that the particle/vesicle shape is complex with the setup therefore we adopted small changes in particle sizes and reported all the results.
  \item Change: We revised Table 1 (page 12) and added Table 2 (page 16) to account for effective properties of vesicles with different size of particles. We added a short description of the new Table 1 in lines 354-359. 
\end{itemize}

\noindent
\comment{The membrane rupture situation, briefly illustrated in Section
4.2.3, is not investigated at all. Is there a dimensionless number
related to this phenomenon with a critical value above which rupture
happens? (e.g.~quantifying the competition between shear and
attraction)}

\noindent
\comment{I understand that the results of Section 4.4 are mostly
qualitative and that the goal is to show the visual agreement between
the coarse-grained and continuum vesicle models, but it would be
insightful to provide quantitative comparisons to measure how close they
are to each other.}
\begin{itemize}
  \item Response: We agree with the Reviewer that we briefly illustrated the capability of simulating membrane rupture via the proposed model and numerical algorithm in the first submission of the manuscript. We further performed a series of study to find the critical shear rate for the appearance of membrane rupture and the corresponding movie is added as a supplementary material. We also included the description in the section of membrane rupture.
  \item Change: We added a short description of vesicle rupture (lines 374-376) in page 13. We added a movie of vesicle rupture (Movie S4) in the supplementary material (page 25).

@@

\item Change: All the modified figures (Figs.~ 9, 10, 11, 12,  13) are made with colorblind friendly colormaps. 
\end{itemize}

\noindent
\comment{Figure 1: the arc length $L$ does not appear in panel (c).}
\begin{itemize}
  \item Change: We deleted the sentence ``$L$ is the arc length''.
\end{itemize}

\noindent
\comment{Line 50: typo: ``well-known"}
\begin{itemize}
  \item Change: This typo is corrected.
\end{itemize}

\noindent
\comment{Page 3: the first two paragraphs seem to be a bit disconnected
from the rest of the introduction. Maybe the authors should rewrite that
part so that there is a transition from the physical problem into
consideration to the various numerical methods used in the literature to
simulate it.}
\begin{itemize}
 \item Response: We thank the referee for pointing this out. We deleted the disconnected paragraph that started with "Brandner...." and modified the end of the following paragraph in response to the next comment from the reviewer.
  \item Change: The paragraph ``Brandner {\it et al} (2019) used the coarse-grained...." is removed.
\end{itemize}

@@

\noindent
\comment{For clarity, use contraction products ``$\cdot$" when a second
order tensor multiplies a vector to avoid confusion (e.g.~${\bf S} \cdot
{\bf F}$ instead of ${\bf SF}$) in eqs.~(3.4), (3.5), (3.7) and so on
$\ldots$}
\begin{itemize}
  \item Change: This notation has been adjusted throughout Section 3.
\end{itemize}

\noindent
\comment{In practice, how do you compute the derivatives $d\sigma /ds$,
$dv_i/ds$ and $dv_i/d\boldsymbol{\nu}$ in (3.13)?}
\begin{itemize}
  \item Response: Since the only derivatives that are required are functions
    defined only on the boundary of the Janus particles, they are
    computed with spectrally-accurate Fourier differentiation.

  \item Change: We have added the following sentence to the start of Section 3
    \begin{quotation}
      All derivatives are computed with spectrally-accurate Fourier
      differentiation.
    \end{quotation}
\end{itemize}

\noindent
\comment{Line 256: you set the strength of the repulsive force $M = 4k_B
T$. In your simulations there is no thermal fluctuations, so why using
$k_B T$ as a reference energy if it is no there in the simulations?
There should be another energy scale that you could use to calibrate
$M$, right?}
\begin{itemize}
\item We thank the reviewer for pointing this out.  This was a typo which has now been corrected. 
\end{itemize}

\noindent
\comment{Related question: how much does the inter-particle distance
depend on on the strength and range of this artificial repulsive
potential? What is the impact on the vesicle shape and effective
properties?}
\begin{itemize}
  \item Response: We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.). The proposed work adopts a different repulsion force from the previous one and we have done studies in choosing the default parameter set to achieve similar structures. For the effective properties, we leave it as a future work.
\end{itemize}

### 2022-02-16 doc/reviews/ResponseToReviewer2.tex

\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{color}
\usepackage{newtxmath}
\newcommand{\comment}[1]{{\color{blue} #1}}

\begin{document}

\noindent
Dear Prof.~Petia Vlahovska,
\\ \\
\noindent
Thank you for handling the manuscript, and we would like to thank the
reviewer for their positive and constructive comments. The attached
manuscript addresses all the reviewer's comments and the result is what
we believe is a stronger manuscript. An itemized list of the changes
addressing the reviewer's comments are below. Changes to the manuscript
from Reviewers 1, 2, and 3 are colored in \textcolor{red}{red},
\textcolor{green}{green}, and \textcolor{magenta}{magenta},
respectively. \\ \\
\noindent
Sincerely,
\\
\noindent
Szu-Pei, Bryan Quaife, Rolf Ryham, and Yuan-Nan Young

\section*{Response to Reviewer 2}
\comment{
\noindent
The authors are introducing a novel numerical approach to study vesicles
under flow conditions in two dimensions. The vesicle is modelled as a
collection of amphiphilic Janus particles (JP) interacting with each
other through a hydrophobic attraction potential (HAP) and a short-range
repulsion force to avoid the overlap between particles. Both the
mobility of the particles and the HAP are recast in the form of an
integral equation of the second kind and solved numerically. The authors
presented some results on the deformation and dynamic of a single
vesicle and a pair of vesicles in different type of external flows.
\\ \\
\noindent
The originality of this work stems from coupling the HAP and Stokes
equations through a boundary integral formulation which I personally
find quite interesting. However, numerical models for vesicles and other
class of soft particles in 2D and 3D are already well established in the
literature. Disregarding the 2D nature of the model, I am not fully
convinced on how this approach outperforms the existing models either in
computational performance or in new applications. The authors should
make an extra effort to highlight this. Another weakness of this model,
if I understood correctly, is that the area of the vesicle is not
conserved beyond the small deformation limit. To the best of my
knowledge, a 2D vesicle should fulfill both constant area and perimeter
constraints. This means that the range of application of the model is
limited to the small deformation limits when used to mimic vesicles
under flow. Finally, this paper lacks a thorough validation of the
numerical results with the existing data in the literature and/or an
original application/result describing a physical phenomenon not covered
by the previous literature. This work is suitable for publication in
this journal but a major revision is needed. Below additional minor
comments to be addressed.}
\begin{itemize}
  \item {\bf Response}: We thank the Reviewer for this positive appraisal of our manuscript.  
The goal of our work, however, is not to provide an alternative vesicle model that outperforms pre-existing continuum models for a lipid bilayer vesicle in the literature. Inspired by de Gennes' suggestion of a thin film from self-assembly of Janus particles, we provide a model for the dynamics of Janus particles that self-assemble into a bilayer (JP vesicle) under various flowing conditions. 
As we showed in the manuscript, there are a lot of similarities between the JP vesicle and the lipid bilayer vesicle reported in the literature.

To highlight both the similarity and difference between our JP vesicle and the lipid bilayer vesicle, we study (1) the hydrodynamics of a JP vesicle in various flow conditions to compare with the corresponding results for a lipid bilayer vesicle,
and (2) we compute the friction between the two JP leaflet, and the permeability of a JP bilayer. We find that the permeability of a JP vesicle allows the total water content enclosed in the JP vesicle to reach an equilibrium value in a flow. We find that the JP vesicle is actually closer to a permeable vesicle that we studied previously, where the 2D vesicle has a constant perimeter but the enclosed area does not stay constant.

In terms of validation of our numerical results of JP vesicle of nano meter size, we have made comparison with the simulations of vesicle of the same size in the literature. For example we compare both the permeability and the inter-leaflet friction coefficient of a JP bilayer membrane with those of a lipid bilayer membrane. We also compare the critical shear rate for rupture between a JP vesicle and a lipid bilayer vesicle. We also compared the hydrodynamics of a JP vesicle and a lipid bilayer vesicle under various flowing conditions. These results are summarized in the original manuscript and re-organized in the revision with better clarity.

Finally we provide a critical capillary number for rupture of a JP vesicle under a linear shear flow. The rupture of a lipid vesicle by a linear shear flow has been reported in experiments.  Our prediction of a critical capillary number and how it scales with various physical parameters of the individual Janus particle is, to our knowledge, not available in the literature. We hope that our results can motivate experimentalist (such as Charles Schroeder who has studied extreme deformation of a vesicle due to an imposed flow) and other theoreticians to study the dynamics of bilayer structures under extreme flowing conditions.

%  \begin{quotation}
%    \noindent
%    Can put verbatim change in this environment.
%  \end{quotation}
\end{itemize}

### 2022-02-16 doc/main_jfm.tex

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  \cite{cawthorn_balmforth_2010} provide the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps are comparable to the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of nm $\text{ns}^{-1}$.
}

>>>>

The base-case is a single JP vesicle consisting of $N_b = 58$ particles
with $c = 0.5 l_0$ for particle radius, $\rho = 2 l_0$ for decay length,
$\gamma = \text{4.1 pN nm}^{-1}$ for interfacial tension.
The parameter $\mu = \text{1 cP} = \text{1 pN
ns nm}^{-2}$ is viscosity of room-temperature water. 
\ReviewerThree{
  We select \ReviewerOne{$M=4.0$~$\text{pN}$} and $\rho_0 = 0.2l_0$ so that \eqref{eq:REPULforce}
  prevents particle collisions and is comparable to hydrodynamic lubrication.
  \citep{cawthorn_balmforth_2010} provide the asymptotic expression 
  $F_{\text{lubr}} = -\tfrac{3}{2}\pi \mu \dot \epsilon (c/\epsilon)^{3/2}$
  for the lubrication force between two cylinders in the distance of separation $\epsilon \to 0$.
  For our choice of simulation parameters, $F_{\text{lubr}}$ and \eqref{eq:REPULforce} are comparable
  because the particle gaps are comparable to the particle radius
  and the relative velocities $\dot \epsilon$ between particles are on
  the order of nm $\text{ns}^{-1}$.
}
